%----------------------------------------------------------------
%
%  File    :  project-listmerger.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  20 Feb 2026
% 
%  Changed :  27 Mar 2026
% 
%----------------------------------------------------------------

\chapter{ListMerger}
\label{chap:listmerger}

\TODO{}

This section describes the implementation of ListMerger. The code itself
is written in pure TypeScript. Almost all third-party librariers are
only used in the build and development process. Only the Mustache
package is used to render templates.

Recurring terms in the development are \uiname{move} and \uiname{merge}.
Moving describes the process of a transferring an item from A merged
item always consists of two predecessors. They are either taken from the
\uiname{mergelist} (merged or moved), or directly taken from the
evaluators list. The origin is always tracked, independent whether The
differentiation between moved and origin is done, to have a clean and
reconstructive merging history. When saving, the order of the merged
elements is taken from the list, while the data about merged is stored
in an array. 


\section{Files}

The TypeScript code is modularised into several files, each serving a
different purpose. The files are:
\begin{itemize}
\item \fname{events.ts}: Initialises all event listeners for buttons
and drag events, and contains their functions.
\item \fname{globalvars.ts}: Contains some shared variables used across several files.
\item \fname{history.ts}: Tracks all actions and recovers them when the \uiname{Undo} or \uiname{Redo} button is pressed.
\item \fname{index.ts}: Serves only as the interface between the module and the outer implementation.
\item \fname{init.ts}: Contains the only function callable from the outside.
\item \fname{transfer.ts}: Handles the transfers between the source lists and the merged list.
\item \fname{uihelper.ts}: Contains several helper functions to deal with the DOM.
\end{itemize}



\section{History (Undo/Redo)}

An important feature and affordance of this component is the history
tracking. With the \uiname{Undo} and \uiname{Redo} buttons, the user can
jump back and forward with actions.

The history is based on a history and a future array. When clicking
undo/redo, a history item is moved from history to future, or vice
versa. A history item consists of a keyword for the action, and three
parameters. The parameters are strings, and can be IDs, or positions,
depending on the context of the merge keyword.


\section{Initialisation}
A detailed guide to the initialisation of a ListMerger instance can be
found in Appendix~\ref{chap:libuser}.



