%----------------------------------------------------------------
%
%  File    :  project-guide-libuser.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  31 Feb 2026
% 
%  Changed :  31 Mar 2026
% 
%----------------------------------------------------------------

\chapter{Library User Guide}
\label{chap:libuser}

This section addresses to those that want to include the ListMerger
library in a larger software project. To initialise a page with lists,
the \vname{init.init()} function needs to be called. The parameters
contain an overall HTML id, the ids for the \uiname{Undo} and
\uiname{Redo} buttons, a function that can be called when the
\uiname{Save} button is clicked, an items object, and several strings
for HTML templates. A full example of a configuration can be seen in the
\fname{example/main.js} file.

Items have to be handed over in an object that needs to contain at least
a \vname{merged} key and an \vname{originlists} key. The first can be an
empty array, or contain items. The second one needs to be filled with
the lists as objects with some metadata (\vname{id}, \vname{name}, etc.)
and an \vname{items} key, which also contains an array of items, as seen
in Listing~\ref{list:itemslist}.


\begin{samepage}
\begin{lstlisting}[%
  float=tp,
  aboveskip=\floatsep,
  belowskip=\floatsep,
  xleftmargin=0cm,              % no extra margins for floats
  xrightmargin=0cm,             % no extra margins for floats
  basicstyle=\footnotesize\ttfamily,
  frame=shadowbox,
  numbers=left,
  language=JavaScript,
  label=list:itemslist,
  caption={[JSON Item Lists]%
Example of an initialising object for items. The items in \vname{merged} are rendered to the \uiname{mergelist}, \vname{originlists} are constructed as lists with the base items.
},
]
{
  "merged": [],
  "originlists": [
    {
      "id": "eval1",
      "name": "List 1",
      "items": [
        {
          "id": "li1it1",
          "title": "Item 1",
          "author": "Martin Rabensteiner",
          "category": "Category 1",
          "images": [
            "images/screenshot1.png",
            "images/screenshot2.png"
          ],
          "description": "This is the first item in the list."
        }
      ]
    }
  ]
}

\end{lstlisting}
\end{samepage}

An item needs to have at least an \vname{id}, this id is also used as id
in the HTML DOM. The other keys are optional and need to be included
depending on whether they are needed in the user-defined templates.
Arrays (like images) are always merged together.

Templates define how the items appear in the lists
(\vname{item_template}), their info modals (\vname{dialog_template}),
and the form to merge two items (\vname{merge_template}). In the merge
form, the \vname{name} attribute needs to be ident with the keys used in
an item. A callback function can be handed over to process the data
further, for example to store it in a database. This function is then
called with an array of moved, and merged items. In the example, the
data just is written to the JavaScript console.


