%----------------------------------------------------------------
%
%  File    :  project-guide-enduser.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  20 Feb 2026
% 
%  Changed :  30 Apr 2026
% 
%----------------------------------------------------------------

\chapter{End User Guide}
\label{chap:enduser}

End users can switch between separated list via tabs, or on more narrow
screens with a select box. Items can be dragged and dropped from one
list on the right to the mergelist on the left. An item is inserted at
the location where it is dropped. The \uiname{Move All} button can be
used to move all existing items of a list to the merged list. The
appearance of items in the list, the info dialog, and the merge dialog
is dependent on the individual implementation.

By dragging one item over another in the mergelist, those items can be
merged. With the drag handle on the right, they can be rearranged.
\uiname{Undo} and \uiname{Redo} let the user jump through the history.
The behaviour of the \uiname{Save} button is given by the individual
implementation.

Next to the tab titles are small numbers that indicate the current state
of the list. For origin lists, they count how much of items have been
added or merged into the mergelist out of the total number per list. For
the mergelist, the indicator shows the total number of items in the
list, not necessarly how much have been added.



\section{Keyboard Shortcuts}
ListMerger offers some shortcuts to ease the use with a keyboard. These shortcuts are:
\begin{itemize}
    \item \liintro{Ctrl + Z}: Undo.
    \item \liintro{Ctrl + Y}: Redo.
    \item \liintro{C}: Collapse all details of elements.
    \item \liintro{M}: Move all remaining elements to the mergelist.
\end{itemize}
