%----------------------------------------------------------------
%
%  File    :  project-userguide.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  20 Feb 2026
% 
%  Changed :  27 Mar 2026
% 
%----------------------------------------------------------------

\chapter{User Guide}
\label{chap:userguide}

\TODO{}


\section{End Users}

End users can switch between separated list via tabs, or on more narrow
screens with a select box. Items can be dragged and dropped from one
list on the right to the mergelist on the left. An item is inserted at
the location where it is dropped. The \uiname{Move All} button can be
used to move all existing items of a list to the merged list. The
appearance of items in the list, the info dialog, and the merge dialog
is dependent on the individual implementation.

By dragging one item over another in the mergelist, those items can be
merged. With the drag handle on the right, they can be rearranged.
\uiname{Undo} and \uiname{Redo} let the user jump through the history.
The behaviour of the \uiname{Save} button is given by the individual
implementation.







\section{Implementors}

This section addresses to those that want to include the ListMerger in a
larger software project. To initialise a page with lists, the
\vname{init.init()} function needs to be called. The parameters contain
an overall HTML id, the ids for the \uiname{Undo} and \uiname{Redo}
buttons, a function that can be called when the \uiname{Save} button is
clicked, an items object, and several strings for HTML templates. A full
example of a configuration can be seen in the \fname{example/main.js}
file.

Items have to be handed over in an object that needs to contain at least
a \vname{merged} key and an \vname{originlists} key. The first can be an
empty array, or contain items. The second one needs to be filled with
the lists as objects with some metadata (\vname{id}, \vname{name}, etc.)
and an \vname{items} key, which also contains an array of items, as seen
in Listing~\ref{list:itemslist}.


\begin{samepage}
\begin{lstlisting}[%
  float=tp,
  aboveskip=\floatsep,
  belowskip=\floatsep,
  xleftmargin=0cm,              % no extra margins for floats
  xrightmargin=0cm,             % no extra margins for floats
  basicstyle=\footnotesize\ttfamily,
  frame=shadowbox,
  numbers=left,
  language=JavaScript,
  label=list:itemslist,
  caption={[JSON Item Lists]%
Example of an initialising object for items. The items in \vname{merged} are rendered to the \uiname{mergelist}, \vname{originlists} are constructed as lists with the base items.
},
]
{
  "merged": [],
  "originlists": [
    {
      "id": "eval1",
      "name": "List 1",
      "items": [
        {
          "id": "li1it1",
          "title": "Item 1",
          "author": "Martin Rabensteiner",
          "category": "Category 1",
          "images": [
            "images/screenshot1.png",
            "images/screenshot2.png"
          ],
          "description": "This is the first item in the list."
        }
      ]
    }
  ]
}

\end{lstlisting}
\end{samepage}

An item needs to have at least an \vname{id}, this id is also used as id
in the HTML DOM. The other keys are optional and need to be included
depending on whether they are needed in the user-defined templates.
Arrays (like images) are always merged together.

Templates define how the items appear in the lists
(\vname{item_template}), their info modals (\vname{dialog_template}),
and the form to merge two items (\vname{merge_template}). In the merge
form, the \vname{name} attribute needs to be ident with the keys used in
an item. A callback function can be handed over to process the data
further, for example to store it in a database. This function is then
called with an array of moved, and merged items. In the example, the
data just is written to the JavaScript console.





\section{Developers}

This section describes the use of this module for developers, using this
plugin as dependency on another project. The code itself is written in
pure TypeScript. Almost all third-party librariers are only used in the
build and development process. Only the Mustache package is used to
render templates.

Recurring terms in the development are \uiname{move} and \uiname{merge}.
Moving describes the process of a transferring an item from A merged
item always consists of two predecessors. They are either taken from the
\uiname{mergelist} (merged or moved), or directly taken from the
evaluators list. The origin is always tracked, independent whether The
differentiation between moved and origin is done, to have a clean and
reconstructive merging history. When saving, the order of the merged
elements is taken from the list, while the data about merged is stored
in an array. 


\subsection{Files}

The TypeScript code is modularised into several files, each serving a
different purpose. The files are:
\begin{itemize}
\item \fname{events.ts}: Initialises all event listeners for buttons
and drag events, and contains their functions.
\item \fname{globalvars.ts}: Contains some shared variables used across several files.
\item \fname{history.ts}: Tracks all actions and recovers them when the \uiname{Undo} or \uiname{Redo} button is pressed.
\item \fname{index.ts}: Serves only as the interface between the module and the outer implementation.
\item \fname{init.ts}: Contains the only function callable from the outside.
\item \fname{transfer.ts}: Handles the transfers between the source lists and the merged list.
\item \fname{uihelper.ts}: Contains several helper functions to deal with the DOM.
\end{itemize}
