%----------------------------------------------------------------
%
%  File    :  project-listmerging.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  20 Feb 2026
% 
%  Changed :  21 Mar 2026
% 
%----------------------------------------------------------------

\chapter{List Merging}
\label{chap:listmerging}

This chapter covers use cases and implementation examples of merged
lists.

\section{Heuristic Evaluations}
The heuristic evaluation is a form of usability inspection, first
described by \textcite{nielsen-he}. A small number of usability experts,
usually 3 to  5, review a user interface and use their judgement and
experience to find potential problems. The evaluation is guided by a
small set of broad principles (the heuristics) for good user interface
design. Outside academic circles, the technique is often known as an
\emph{expert review}. \textcite{andrews-hci} describes the ideal process
of a heuristic evaluation with five phases: Preparation, Individual
Evaluations, Aggregation, Severity Ratings, and Debriefing and Report.
The essential steps of list merging are the second and third. In the
Individual Evaluations phase, the evaluators observe the interface
completely independent and described the issues found by them. In the
Aggregation phase afterwards, an evaluation manager needs to aggregate
these findings and combine similar ones. Therefore, the evaluation
manager must be able to simple combine the issues with all their
metadata (heuristic, description, attached screenshots, and so on) Those
are then further rated according to their severity and described in a
report.



\section{Acquisition Lists}
Different departments or employees can enter their needs and wishes for
supplies. An acquisition manager has then an overview of all wishes.
Identical or similar items can be combined and the quantity of the
concerning item increased.



\section{Recipes}
Recipes would be use case where similar items in different lists would
be beneficial and desirable. The origin lists are for recipes selected
by the prospective cook. In the merged list, the needed or the already
available ingredients can be gathered. This highlights overlapping
ingredients in recipes and helps to depict which recipes can be cooked
with the available ones or which ones need to be bought.

