%----------------------------------------------------------------
%
%  File    :  project-webtech.tex
%
%  Author  :  Martin Rabensteiner
% 
%  Created :  31 Mar 2026
% 
%  Changed :  31 Mar 2026
% 
%----------------------------------------------------------------

\chapter{Modern Web Technologies}
\label{chap:webtech}

\TODO{}

The main browser vendors united already in 2004 as Web Hypertext
Application Technology Working Group (WHATWG), but the definition of the
HTML standard was in charge of the World Wide Web Consortium (W3C) for
some decades. In 2018, the browser vendors became mutinous and only one
year later, both signed an agreement where W3C is giving the vendors
more say \parencite{cimpanu-whatwg-w3c}. This led to more
standardization among different browsers, and a faster drive of
innovation, like the improvements mentioned as follows.


\section{Living HTML}
The Hyper Text Markup Language (HTML) standard was first developed and
published in the early 1990's by Tim Berners-Lee at CERN and later
handed over to the new founded World Wide Web Consortium
(W3C)~\ref{whatwg-livingstandard}. The last major version (HTML4) was published in
1998, and after some intermediate versions, the work on HTML5 started by
W3C in 2004. Since the dispute between W3C and the browser vendors, 

\section{Modern CSS}
Along with the HTML modernisation, the Cascading Style Sheets (CSS)
became a living standard as well \parencite{w3c-css}. CSS is used to
define to optical style of a website. Modern solutions include for
example containers queries \parencite{mdn-cssquieries} to differentiate
between different screen sizes or use styles as selectors, or color
mixing functions \parencite{mdn-colorfunctions}.

\section{Modern JavaScript}
% Node.js
% jQuery
% selectors
% event handling
\parencite{shukla-jsfullstack}


JavaScript is essential in modern web development to make client-site
computations and modify the Document Object Model (DOM), which describes
the structure and content of a web page. It was introduced in 1995, soon
available in all usual browsers, and is and still today an important
component of them. As dynamic web pages become more and more popular, it
was even more necessary to manipulate the content directly on the
client.


\section{Node.js}
With Node.js, it became popular to use JavaScript also as a server-side
programming language. 
% Todo Node paragraph


\section{jQuery}
jQuery is a widley-used frontend framework and reached its peak of usage
on around 78 \% of all websites tracked in 2022 and is steadly
decreasing since then, with circa 70 \% in March 2026
\parencite{w3techs-js-statistics}. By time, the outstanding functions of
jQuery got more and more redundant. Several use cases and
functionalities were integrated directly in HTML, CSS, or JavaScript.
For example, the accordion can now be replaced with the
\elname{details} tag (available since 2020)
\parencite{mdn-html-details}. JavaScript introduced selector functions
like \vname{querySelector()}, \vname{querySelectorAll()} and some other
for HTML element in 2015 \parencite{mdn-js-queryselector}. This made the
classic jQuery DOM selection with the {\vname{\$()}} function obsolete.

% paragraph to top?





\section{JavaScript Package Managers}

The node package manager (NPM) was introduced in 2009, to make the
handling with node modules in the development process and their
publishment among developers more convenient. It is an open source
project and now in the hands of GitHub \parencite{npm-website}.

% Yarn

PNPM (performant NPM) introduces a more performant approach for package
managing than NPM \cite{pnpm-website}. Instead of downloading and
storing dependencies for every project on its own, they are managed
globally on the system, and symbolic links are created from the project
to the main storage. That saves time and storage space. Further, PNPM is
capable of managing different versions of Node. For other package
managers, a separate Node Version Manager is needed. Disadvantages arise
when multiple disks are used on a system, as the symlinks used by PNPM
are not capable of that.

To measure the popularity of package managers, \textcite{maj-article}
discusses different ways to count the usage. Different ways of downloads
have the problem of different sources, and packager managers with more
frequent updates will have higher download counts. The observation of
the most popular GitHub repositories is considered a meaningful
measurement. According to the last iteration \cite{maj-repository} and
compared with the last three years, NPM is steadily used in about two
third of projects. The usage of Yarn classic has decreased from 29 \% to
18 \% over the same time frame. PNPM has a stagnant share of about 6 \%.

PNPM is used in this project to combine its advantages in speed and
storage performance with 



\section{GitHub Pages}
\TODO{}


\section{Mustache Templates}
Mustache is a logic-less template format \parencite{mustache}.
Characteristic are the double \vname{\{\{\}\}} brackets, which are then
replaced. For example, \vname{\{\{variable\}\}} is replaced with the
value of \vname{variable}. For-each loops and simple if conditions can
be mocked with Mustache, even though there is no logic in the template.
Mustache libraries are available for around 50 programming languages,
including JavaScript, Python, PHP, or C++. It is popular to structure
small or large parts of content with its template style.

\section{Accessibility}
\label{sec:accessibility}
% chap about accessibility in general
